---
title: "MSEP Water Quality Working Group survey responses"
format: 
    html:
        toc: true
        embed-resources: true
        warning: false
        message: false
        echo: false
date: today
---

```{r}
library(tidyverse)
library(readxl)
# library(gt)
library(tinytable)

source(here::here("R", "definitions.R"))

in_file <- here::here("input",
                      "2026-02-06 MSEP WQ Working Group Interest (Responses).xlsx")


```
```{r}
#| label: yellow-orange highlighting-msepcols


# yellows: lightest first
yellows <- khroma::color("YlOrBr")(9)

# header
color_colnames <- "#20434a"
# color_colnames <- "#225555"

# background and colors 1
color_background1 <- yellows[2]
color_text1 <- "#20434a"

# background and colors 2
color_background2 <- yellows[3]
color_text2 <- "#20434a"
```

```{r}
# set up tinytable to make things a little easier
my_tt <- function(data){
    tt(data) |> 
        style_tt(i = 0,
                 color = color_colnames,
                 bold = TRUE) |> 
        style_tt(j = 2,
                 align = "r")
}
```


```{r}
dat_in <- read_xlsx(in_file)

# general tidying
dat <- dat_in |> 
    select(-Timestamp) |> 
    rename_with(~ name_map[.x], .cols = any_of(names(name_map))) |> 
    mutate(Participation = define_participation(Participation),
           Organization_general = simplify_organization(Organization),
           Techniques = str_remove_all(Techniques, " \\([^)]*\\)"),
           Involvement = str_remove_all(Involvement, " \\([^)]*\\)"),
           Topics = str_remove_all(Topics, " \\(e.g. CDOM, TSS, Turbidity\\)"))



# split into different 'response variables' of interest
dat_involvement <- dat |> 
    select(Name, Organization, Involvement) |> 
    mutate(Involvement = str_split(Involvement, 
                                   paste0("(?<=", paste(categories_involvement, collapse = "|"), "), "))) %>%
    unnest(Involvement)


dat_techniques <- dat |> 
    select(Name, Organization, Techniques) |> 
    mutate(Techniques = str_split(Techniques, 
                                   paste0("(?<=", paste(categories_techniques, collapse = "|"), "), "))) %>%
    unnest(Techniques)


dat_topics <- dat |> 
    select(Name, Organization, Topics) |> 
    mutate(Topics = str_split(Topics, 
                                   paste0("(?<=", paste(str_escape(categories_topics), collapse = "|"), "), "))) %>%
    unnest(Topics) |> 
    mutate(Topics = case_when(Topics == "pH/Ocean acificiation" ~ "pH/Ocean acidification",
                              .default = Topics))
```

```{r}
# summarize data frames by variables of interest
summ_involvement <- summarize_categories(dat_involvement, Involvement, categories_involvement) |> 
    rename(Count = n)

summ_techniques <- summarize_categories(dat_techniques, Techniques, categories_techniques) |> 
    rename(Count = n)

summ_topics <- summarize_categories(dat_topics, Topics, categories_topics) |> 
    rename(Count = n)


# summarize by how many choices each user checked
users_involvement <- dat_involvement |> 
    summarize(.by = Name,
              n_choices = n()) |> 
    count(n_choices) |> 
    rename(`# Selected` = n_choices,
           Count = n)

users_techniques <- dat_techniques |> 
    summarize(.by = Name,
              n_choices = n()) |> 
    count(n_choices) |> 
    rename(`# Selected` = n_choices,
           Count = n)

users_topics <- dat_topics |> 
    summarize(.by = Name,
              n_choices = n()) |> 
    count(n_choices) |> 
    rename(`# Selected` = n_choices,
           Count = n)
```

```{r}
# get information about all the "Other" selections
other_involvement <- dat_involvement |> 
    filter(!(Involvement %in% categories_involvement))

other_techniques <- dat_techniques |> 
    filter(!(Techniques %in% categories_techniques))

other_topics <- dat_topics |> 
    filter(!(Topics %in% categories_topics))
```


## Summaries of roles and interests  

### What's your role?  

#### How many boxes did each person check?  

```{r}
t <- my_tt(users_involvement) |> 
            style_tt(j = 1,
                 align = "c")  
t
```

```{r}
t2 <- t |> 
    style_tt(i = 1,
             background = color_background1,
             color = color_text1,
             bold = TRUE)
t2
```


#### What were the selections?  

```{r}
t <- my_tt(summ_involvement) |> 
            style_tt(j = 1,
                 align = "l") 
t
```

```{r}
t2 <- t |> 
    style_tt(i = 1,
             background = color_background1,
             color = color_text1,
             bold = TRUE) 
t2
```

The 'Other' answers included:  

-  Coordinating collaborations/Running working groups (2)  
-  Laboratory work (2)
-  WQ Assessment
-  Extension  
-  Water Resource Planning  
-  Work with seabirds  

***  


### What techniques do you use?  

#### How many boxes did each person check?  

```{r}
t <- my_tt(users_techniques) |> 
            style_tt(j = 1,
                 align = "c") 
t

```

```{r}
t2 <- t |> 
    style_tt(i = 1:3,
             background = color_background1,
             color = color_text1,
             bold = TRUE) 
t2
```


#### What were the selections?  

```{r}
t <- my_tt(summ_techniques) |> 
            style_tt(j = 1,
                 align = "l") 

t
```

```{r}
t2 <- t |>  
    style_tt(i = 1:2,
             background = color_background1,
             color = color_text1,
             bold = TRUE) 

t2
```

```{r}
t2 |> 
    style_tt(i = 3,
             background = color_background2,
             color = color_text2,
             bold = TRUE) 
```

The 'Other' category included:  

-  Volunteer monitoring (2)  
-  Fecal coliform and algae identification and enumeration  
-  Restoration and nutrient reduction  
-  left blank (3)  

***  

### What topics do you work with?  

#### How many boxes did each person check?  

```{r}
t <- my_tt(users_topics) |> 
            style_tt(j = 1,
                 align = "c") 
t
```

```{r}
t2 <- t |> 
    style_tt(i = c(2, 3, 7),
             background = color_background1,
             color = color_text1,
             bold = TRUE)
t2
```


#### What were the selections?  

```{r}
t <- my_tt(summ_topics) |> 
            style_tt(j = 1,
                 align = "l") 
t
```

```{r}
t2 <- t |> 
    style_tt(i = 1:6,
             background = color_background1,
             color = color_text1,
             bold = TRUE) 
t2
```

```{r}
t2 |> 
    style_tt(i = 7:10,
             background = color_background2,
             color = color_text2,
             bold = TRUE)
```

The 'Other' category included:  

-  SAV  


